\documentclass[ppgc,diss,english]{iiufrgs}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{times}  
\usepackage[alf,abnt-emphasize=bf]{abntex2cite}

\usepackage{amsfonts}
%\usepackage[numbers]{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tocbibind}
\usepackage[lined, linesnumbered]{algorithm2e}
\usepackage{array}
\usepackage{makecell}
\usepackage{tikz}
\usepackage{lscape}
\usepackage{caption}
%\usepackage{cite}
\usepackage{subcaption}
\usepackage{marginnote}
\usepackage{todonotes}

\usepackage{ifdraft}
\usepackage[all]{xy}
\usepackage[titletoc]{appendix}

\usetikzlibrary{positioning,arrows}
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother

\title{Branch \& Price for the Virtual Network Embedding Problem}
\author{Moura}{Leonardo F.S.}
\advisor[Prof.~Dr.]{Buriol}{Luciana}
\date{}{2015}
\keyword{Branch \& Price}
\keyword{Virtual Network Embedding}
\keyword{Network Virtualization}
\keyword{Exact Algorithms}

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}
\newcommand{\todoc}[1]{\todo[color=red!20, bordercolor=white]{#1}}
\newcommand{\todoi}[1]{\todo[inline,color=red!20, bordercolor=white]{#1}}

%\setcounter{tocdepth}{1}

\begin{document}

\maketitle

\chapter*{Acknowledgments}
First I would like to thank my advisor Luciana Buriol for accompanying me since the inception of my academic career.
With her help I have grown so much as a person and as a professional. 
An equal share of thanks goes to my former advisors Marcus Ritt, Aline Villavicencio, and Van-Dat Cung.
Their guidance was essential in my academic success.

Without my parents, Raquel and Vitor, I would not have made it this far.
A sincere thanks to all my friends for all their support and for putting up with me during difficult times.

A special thanks is due to my research group colleagues --- Leonardo, Paulo, Marcelo, Tadeu, André, Germano, Renato, Alex, Fernando, and Arton ---
for all their help, either by discussing technical, theoretical or personal issues.
Many thanks to all the organizers of ELAVIO 2014, there I learned a lot and made good friends for life.

This work was supported by CNPq (Brazilian National Research Council) and by Instituto de Informática da UFRGS.

\begin{abstract}
Virtualization allows one or more virtual networks to share physical infrastructures.
The Virtual Network Embedding problem (VNEP) is one of the main challenges in the virtualization of physical networks. 
This problem consists in mapping a virtual network into a physical network while respecting capacity constraints.
This work shows that finding a feasible solution for this problem is NP-Hard.
However, many instances can be solved up to optimality in practice by exploiting the problem structure.
%In this work we use a flow-based formulation of the problem and solve the relaxation using a
%column generation approach. 
%This method results in high quality lower bounds obtained in short time, as the computational experiments show.
%This suggests that it can be successfully embedded in a branch \& price method for providing optimal solutions for the VNEP.
We present a Branch \& Price algorithm applied to instances of different topologies and sizes.
The experimental results suggest that the proposed algorithm is superior to the Integer Linear Programming model solved by CPLEX.
\end{abstract}

\begin{englishabstract}{Branch \& Price para o Problema de Mapeamento de Redes Virtuais}{Problema de Mapeamento de Redes Virtuais. Programação Linear Inteira. Geração de Colunas. Algoritmos Exatos}
Virtualização permite o compartilhamento de uma rede física entre uma ou mais redes virtuais.
O Problema de Mapeamento de Redes Virtuais é um dos principais desafios na virtualização de redes.
Esse problema consiste em mapear uma rede virtual em uma rede física, respeitando restrições de capacidade.
O presente trabalho mostra que encontrar uma solução factível para esse problema é NP-Difícil.
Mesmo assim, muitas instâncias podem ser pode ser resolvidas na prática através da exploração de sua estrutura.
Nós apresentamos um algoritmo de Branch \& Price aplicado a instâncias de diferentes topologias e tamanhos.
Os experimentos realizados sugerem que o algoritmo proposto é superior ao modelo de programação linear resolvido com CPLEX.
\end{englishabstract}

\listoffigures

\listoftables

\listofalgorithms
\addcontentsline{toc}{section}{LIST OF ALGORITHMS}

\begin{listofabbrv}{VNEP}
        \item[VNEP] Virtual Network Embedding Problem
        \item[UFP]  Unsplittable Flow Problem
        \item[ILP]  Integer Linear Program
        \item[B\&P] Branch \& Price
        \item[B\&B] Branch \& Bound
        \item[RMP]  Restricted Master Problem
        \item[CG]   Column Generation
\end{listofabbrv}

%\addcontentsline{toc}{subsection}{Preface}
%\tableofcontents*
\newpage

\chapter*{Contents}
\makeatletter
\@starttoc{toc}
\makeatother

\input{introduction.tex}

\input{relwork.tex}

\input{problem.tex}

\input{cg.tex}

\input{bp.tex}

\input{results.tex}

\input{conclusion.tex}

%\bibliography{VNE}
%\bibliographystyle{plainnat}
\bibliographystyle{abntex2-alf}
\bibliography{VNE}

\input{appendix.tex}

\end{document}
